The Tail Risk Premium - Extension of Lottery Preference Premium

### 2025-02-26 paper.qmd
Added Paper
Updates To Paper

---
title: "The Tail Risk Premium - Extension of Lottery Preference Premium"
format: html

@@

>>>>

---
title: "The Tail Risk Premium - Extension of Lottery Preference Premium"
format: html
author: "Brayden Boyko, Roan Henderson, Andrew Pettifor"
jupyter: 
    kernel: python3

@@

```{Python}
#| echo: false
#| warning: false

```

## Performance Evaluations
A variety of benchmark statistics will be included in our portfolio testing:
+ Annual / Monthly Return Values/Charts For 4 Portfolios
+ Describe Stock Breakdown For Four Portfolios (Skew, IVOL)
+ V1 & V2 Screening
